Reduced GW invariants from cuspidal curves

### 2017-12-13 draft.tex
added genus one CM singularities

In particular the space $\overline{\pazocal{M}}^{(1)}_{1,n}(\PP^r,d)$ we will be interested in the next sections does not have the boundary divisor $D_{d,n}(\PP^r,d).$
% \begin{cor}\cite[Cor.~5.10]{VISC}
% For $m\geq\operatorname{min}(r,d)+n$, $\overline{\mathcal{M}}^m_{1,n}(\PP^r,\beta)$ is irreducible.
 %\end{cor}

\begin{comment}
 Moreover, inspired by Viscardi's alternate compactification, we express a sufficient condition for smoothability in yet another way.
 \begin{prop}
Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a ($n$-marked) genus one curve of the form $(E {}_{p_1,\ldots,p_m}\sqcup_{q_1,\ldots,q_m}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus one subcurve, and $R_i$ are the rational tails (chains of $\PP^1$ along which $f$ has positive degree). 
 If $f$ factorises through a \emph{non-degenerate} (i.e. having positive degree along at least one of the branches of the singularity) map $f'\colon C'\to\PP^r$ from an elliptic $k$-fold singularity, with $k\leq m$, then  $\operatorname{d}\!f(T_{q_i}R_i)$ are linearly dependent in $T_{f(E)}\PP^r$.
 \end{prop}
 \begin{proof}
 Let $\xymatrix{C\ar[r]^{\pi} &C'\ar[r]^{f'} &\PP^r}$ be the factorization of $f$. Then $E'=\operatorname{Exc}(\pi)\subseteq E$ and 
  $\overline{C\setminus E'}=(S_1,q'_1)\sqcup\dots\sqcup (S_k,q'_k)\to (C',p)$ 
  is the normalization of the elliptic $k$-fold point. By hypothesis, $f=f'\circ\pi$ and $f$ is non-constant on $R_1,\dots R_m.$ Being $f'$ non-degenerate implies that there exists a subset
  $\left\{S_1,\ldots S_j\right\}\subseteq\left\{S_1,\ldots S_k\right\}$ 
  such that \[(S_1,q'_1)\cong (R_{i_1}, q_{i_1}),\ldots, (S_j,q'_j)\cong (R_{i_j}, q_{i_j}),\;\;\left\{i_1,\dots,i_j\right\}\subseteq \left\{1,\dots,m\right\}.\] 
By Smyth's characterisation of elliptic $k$-fold singularities, \cite[Lem.~2.2]{SMY1}, we obtain a non trivial linear relation 
  \begin{equation*}
  \label{eq:dep}\alpha_1\operatorname{d}\!\pi(T_{q_{i_1}}R_{i_1})+\ldots+\alpha_j \operatorname{d}\!\pi(T_{q_{i_j}}R_{i_j})+\alpha_{j+1}\operatorname{d}\!\pi(T_{q_{j+1}}S_{j+1})+\ldots+\alpha_k \operatorname{d}\!\pi(T_{q_k}S_k)=0
  \end{equation*}
  since all the coefficients are non-zero, $j\neq0$, and the second half of the formula can be ignored, we've got what we wanted.
  \end{proof}
\begin{rem}\label{remark:cuspunionline} 
The viceversa is not true, as Remark \ref{remark:sprouting} shows.
\end{rem}

@@

It is a matter of fact that the virtual dimension of the moduli space of maps to a three-fold $X$ is independent of the genus. In this context it was plausible to test the better enumerative properties of reduced invariants; in fact, Li-Zinger \cite{LZ} in the symplectic category and, later on, Chang-Li \cite{CL} in the algebraic one, proved a comparison formula for the quintic three-fold $X_5\subseteq\PP^4$ (or, more generally, for a complete intersection three-fold $X$ of degree $(l_1,\ldots,l_k)$ in $\PP^r$ with $\sum l_i\leq r+1$) of the form
$$GW_1(X)=\widetilde{GW}_1(X)+c\cdot GW_0(X).$$
We notice that the genus zero contribution to this formula comes from the boundary component with a single rational tail of degree $d$, while elliptic bridges and degenerate contributions with more rational tails do not matter to the genus one Gromov-Witten count. This suggests that removing the component with elliptic tails would provide a more direct and efficient definition of reduced invariants. We plan to do so by comparing the ordinary space of stable maps with Viscardi's space of 1-stable maps.
\end{comment}
\section{Cuspidal curves and maps}

In this section we start investigating the Gromov- Witten type invariant obtained from Viscardi compactification studying the case $m=1$: the source curve is at worst cuspidal. We will see how in this case we can give a comparison with the GW-invariant and explain why the same technique does not work for higher $m$.
The first thing we do is the following:
we introduce a moduli space of stably-weighted, prestable, at worst cuspidal, marked curves. We show that there is a birational morphism from a correspondingly decorated moduli space of prestable nodal curves. Taking the fiber product with Viscardi's moduli space of stable cuspidal maps, we show that the resulting space includes in the usual Kontsevich's moduli space, precisely avoiding the component with elliptic tails $D_{\{d\},\{n\}}(X,d)$.

Why should such a morphism on decorated prestable curves exist? 
Consider an elliptic tail $C$; a one-dimensional family $\mathcal C$  with central fiber $\mathcal C_0\cong C$ will either be locally constant or smoothen the node. In the first case we can associate to this the locally constant family of cusps obtained by forgetting the elliptic tail and contracting a length-two infinitesimal neighborhood of the node in the rational component; in the second case, we claim that the line bundle $\mathcal O_\mathcal C(3q)$ gives a morphism to a smoothing of the cuspidal $\PP^1$. This heuristics (i.e. being able to substitute an elliptic tail with a cusp over points or DVR schemes) motivates us to believe we can define a morphism from suitably defined moduli spaces of nodal genus one curves to cuspidal curves (cfr. \cite[Lemma 4.2]{SMY2}). In fact we shall extend \cite[Corollary 4.5]{SMY2} to an appropriate setup of moduli stacks of weighted prestable curves. Assume $d>0$ throughout the following.

@@

\section{Local equations and desingularisation}\label{sec:equations}
\subsection{Notation}
Let $\Z$ be defined by the pullback diagram:
\bcd
\mathcal Z \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
\mathfrak M_1^{\rm{wt}}\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
\ecd

@@

We introduce some more notation: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
\bcd
\mathcal Z^p \ar[r,"\alpha"]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
\XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1^{(1)} \ar[d] \\
\X\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
\ecd

@@

\begin{cor}
$\deg[\Z^p]^{\rm{vir}}_{\rm{loc}}=\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}$
\end{cor}
\subsection{Equations for $\Z^p$ relative to $\XP$}
We are going to need a description of the normal cone $\mathfrak C_{\Z^p/\XP}$ in order to perform a splitting.

>>>>

In particular the space $\overline{\pazocal{M}}^{(1)}_{1,n}(\PP^r,d)$ we will consider in the next sections does not have the boundary divisor $D_{(d),(n)}(\PP^r,d).$
% \begin{cor}\cite[Cor.~5.10]{VISC}
% For $m\geq\operatorname{min}(r,d)+n$, $\overline{\mathcal{M}}^m_{1,n}(\PP^r,\beta)$ is irreducible.
 %\end{cor}
 \subsection{A different characterization of smoothability}
 Inspired by Viscardi's alternate compactification, we give yet another characterisation of smoothable maps in genus $1.$
 \begin{dfn}
 Let $C$ a reduced curve and $p\in C$ a singular point, we define the genus of the singularity in $p$ to be the quantity: $g(p)=\delta(p)-b(p)+1.$  We are using the following notation: $\delta(p)=\dim_k\OO_{\overline C}/\OO_C,$ $\overline{C}$ being the normalization of $C$; $b(p)$ is the number of branches at $p.$
 \end{dfn}
 \begin{prop}\label{prop:smoothability2}
 Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a $n$-marked genus $1$ curve $(E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus $1$ subcurve, and $R_i$ are rational tails.

  Then $f$ is smoothable if and only if it factors through a Cohen-Macaulay genus $1$ singularity with positive degree on at least one of its branches.
\end{prop}

\begin{lem}(Classification of CM genus $1$ singularities)
The  Cohen-Macaulay genus $1$ singularities with $m$ branches are all and only obtained by gluing a genus $0$ singularity with $k$ branches with a Smyth's $m-k$-elliptic fold.
Notice that $k$ may be $0$ (i.e. a point) or $1$ (i.e. a smooth rational curve).
\end{lem}
\begin{proof}
The proof follows the technique already used by Smyth \cite[Appendix~A]{SMY1} to classify the Goreinstein genus $1$ singularities. The question of classifying singularities in local analytic, so as in \cite[Appendix~A]{SMY1} we use the following notation:
$R$ denote the analytic local ring of the singularity; 
$\widetilde{R}=k[[t_1]\oplus\dots\oplus k[[t_m]]$ its integral closure; $\mathfrak{m}_R$ is the maximal ideal in $R$  and $\mathfrak{m}_{\widetilde{R}}$ the maximal ideal in $\widetilde{R}.$

Let us recall that to describe $R$ as a polynomial ring, it is enough to find a basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=(e_1,\dots e_s)$ where the $e_i$ are some regular functions in $\widetilde{R}.$ Indeed, once given such a basis, $R$ can be recognized as $k[x_1,\dots x_s]/I$ where $I$ is the kernel of the ring homomorphism
\begin{align}\label{eq:singularity}
k[[x_1,\dots x_s]]&\rightarrow R\subset k[[t_1]\oplus\dots\oplus k[[t_m]]\\
\;\;x_i\;\; &\rightarrow \;\; e_i.\;\;
\end{align}
It has been observed by Smyth \cite[Proposition~A.3]{SMY1} that $R$ being the local ring of a genus $1$ singularity implies:
\[\mathfrak{m}^2_{\widetilde{R}}\subset R,\qquad \mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak{m}_{\widetilde{R}}/\mathfrak{m}^2_{\widetilde{R}}\;\;\text{is codimension $1$},\]
which allows him to say that, after Gauss elimination, we have $e_1,\dots e_{m-1}$ generators of $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$ of the following form
\begin{align*}
e_1=& (t_1 \,0\dots\,0\, a_1 t_m)\\
e_2=&( 0\,t_2\,0\dots\, a_2 t_m)\\
&\dots\\
e_{m-1}=&(0\dots\,t_{m-1}\, a_{m-1}t_m ).
\end{align*}
with $a_{1},\dots, a_{m-1}\,\in \k.$ At this point Smyth restricts his attention on Gorenstein singularities and he shows that under the Gorenstein assumption and when $m\geq 3$: we can choose all the $a_i$ to be $1$; $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ and thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we are  done.
Otherwise we have:

\noindent{For $m\geq 3$} three possibilities:
\begin{enumerate}
\item At least two of the $a_i$ are non zero.
\item Only one of the $a_i$ is non zero
\item All the $a_i$ are zero
\end{enumerate}
\noindent{For $m=23$} two possibilities
\item $a_1$ is non zero, then we have the tacnode;
\item  $a_1$ is zero
\noindent{For $m= 1$} As in Smyth's we prove that in this  case $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}_{R}$ which means the singularity is a cusp. 
\end{proof}
\begin{lem}
All of the Cohen-Macaulay genus ~$1$ singularities are smoothable.
\end{lem}
\begin{proof}
We prove this statement by exhibiting an explicit smoothing for this singularities.
Start considering two families $\cC^0\to T$ and $\cC^1\to T$ respectively of smooth rational curves and smooth elliptic curves, with $T$ a DVR scheme, e.g. consider two trivial families.

 Then blow up respectively $k$ smooth points $p_1,\dots p_k$ and  $m-k$ smooth points $q_{k+1},\dots q_{m-k}$ on the central fibers  $(\cC^0)_0$ and $(\cC^1)_0.$

On  $\widetilde{\cC}^0\xrightarrow{\pi_0} \cC^0\to T$ and $\widetilde{\cC}^1\xrightarrow{\pi_1} \cC^1\to T$ there exist $\pi_0$, respectively $\pi_1$ semi-ample line bundles which are trivial on the proper transform of the central fibers and very ample every where else.
If we started with the trivial families we can take \begin{align*}
\mathcal L_0&=\pi_0^*\OO_{\cC^0}(p_1\times T+\dots+ p_k\times T)(-F_1-\dots -F_k),\\
 \mathcal L_1&=\pi_1^*\OO_{\cC^1}(q_{k+1}\times T+\dots+ q_{m-k}\times T)(-F_{k+1}-\dots -F_{m-k})
\end{align*}
where we denoted by $F_j$ the exceptional divisors of both the blow ups.
We can then contract respectively  $\;\pi_0^*(\cC^0)_0(-F_1-\dots -F_k)\;$ and $\;\pi_1^*(\cC^1)_0(-F_{k+1}-\dots -F_{m-k}).$

The contracted families   $\;\hat{\cC}^0\to T\;$ and $\;\hat{\cC}^1\to T\;$ have still generic smooth fibers of genus $0$ and $1$ respectively and, by construction: $(\hat{\cC}^0)_0$ has a genus $0$ singularities with $k$ branches and $(\hat{\cC}^)_0$ has an $m-k$ elliptic curves\cite[Lemma~2.12]{SMY1}.

Choose $\sigma_0$ and $\sigma_1$ two sections of $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ passing through the singular points in the central fibers and let $\hat{\cC}\to T$ the family of curves obtained identifying $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ along $\sigma_0$ and $\sigma_1$, endowed with their reduced structures.
Then $\hat{\cC}$ has nodal generic fiber and one of our genus 1 singularities as central fibers.

Choose now a simultaneous smoothing of the generic fiber, e.g. if the families were trivial this is clearly possible; a generic direction of the two parameter family obtained this way is a smoothing of our singularity.
\end{proof}

\begin{proof}\ref{prop:smoothability2}
 The argument to prove that if $f$ is smoothable then it has to factors through a genus $1$ singularity is exactly the same used by Vakil to show that the tangent vectors have to be linearly dependent in the image and thus we do not repeat it but we refer the reader to \cite{Vre}.

Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C} $a genus $1$ singularity. Let $\hat{\cC}$ be a smoothing of $\hat{C}$ and $\hat{\mathcal L}$ an extension of $\hat{L}:=\hat{f}^*\OO_{\PP^r}(1)$ on the smoothing, which exists because deforming line bundles on curves is unobstructed. Then all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0.$

Since all the curve we are considering are Cohen-Maculay, they have a dualising pure sheaf $\omega_{\hat{C}}.$

  \end{proof}

\begin{remark}
It is not hard to adapt Vakil's argument \cite{Vre} to show that factoring through a genus $1$ singularity is equivalent to the tangent vectors being linearly dependent in the image.
\end{remark}
\begin{remark}
The ideas above are similar to those employed in \cite[Theorem 4.5.1]{RSPW} to show that $\pazocal{VZ}_{1,n}(\PP^r,d)$ is smooth, where the latter is defined by requiring the factorisation property for the map through a Smyth's singularity after sprouting.
\end{remark}

\begin{comment}
 Moreover, inspired by Viscardi's alternate compactification, we express a sufficient condition for smoothability in yet another way.
 \begin{prop}
Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a ($n$-marked) genus one curve of the form $(E {}_{p_1,\ldots,p_m}\sqcup_{q_1,\ldots,q_m}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus one subcurve, and $R_i$ are the rational tails (chains of $\PP^1$ along which $f$ has positive degree). 
 If $f$ factorises through a \emph{non-degenerate} (i.e. having positive degree along at least one of the branches of the singularity) map $f'\colon C'\to\PP^r$ from an elliptic $k$-fold singularity, with $k\leq m$, then  $\operatorname{d}\!f(T_{q_i}R_i)$ are linearly dependent in $T_{f(E)}\PP^r$.
 \end{prop}
 \begin{proof}
 Let $\xymatrix{C\ar[r]^{\pi} &C'\ar[r]^{f'} &\PP^r}$ be the factorization of $f$. Then $E'=\operatorname{Exc}(\pi)\subseteq E$ and 
  $\overline{C\setminus E'}=(S_1,q'_1)\sqcup\dots\sqcup (S_k,q'_k)\to (C',p)$ 
  is the normalization of the elliptic $k$-fold point. By hypothesis, $f=f'\circ\pi$ and $f$ is non-constant on $R_1,\dots R_m.$ Being $f'$ non-degenerate implies that there exists a subset
  $\left\{S_1,\ldots S_j\right\}\subseteq\left\{S_1,\ldots S_k\right\}$ 
  such that \[(S_1,q'_1)\cong (R_{i_1}, q_{i_1}),\ldots, (S_j,q'_j)\cong (R_{i_j}, q_{i_j}),\;\;\left\{i_1,\dots,i_j\right\}\subseteq \left\{1,\dots,m\right\}.\] 
By Smyth's characterisation of elliptic $k$-fold singularities, \cite[Lem.~2.2]{SMY1}, we obtain a non trivial linear relation 
  \begin{equation*}
  \label{eq:dep}\alpha_1\operatorname{d}\!\pi(T_{q_{i_1}}R_{i_1})+\ldots+\alpha_j \operatorname{d}\!\pi(T_{q_{i_j}}R_{i_j})+\alpha_{j+1}\operatorname{d}\!\pi(T_{q_{j+1}}S_{j+1})+\ldots+\alpha_k \operatorname{d}\!\pi(T_{q_k}S_k)=0
  \end{equation*}
  since all the coefficients are non-zero, $j\neq0$, and the second half of the formula can be ignored, we've got what we wanted.
  \end{proof}

  \begin{rem}\label{remark:cuspunionline} 
The viceversa is not true, as Remark \ref{remark:sprouting} shows.
\end{rem}

@@

It is a matter of fact that the virtual dimension of the moduli space of maps to a three-fold $X$ is independent of the genus. In this context it was plausible to test the better enumerative properties of reduced invariants; in fact, Li-Zinger \cite{LZ} in the symplectic category and, later on, Chang-Li \cite{CL} in the algebraic one, proved a comparison formula for the quintic three-fold $X_5\subseteq\PP^4$ (or, more generally, for a complete intersection three-fold $X$ of degree $(l_1,\ldots,l_k)$ in $\PP^r$ with $\sum l_i\leq r+1$) of the form
$$GW_1(X)=\widetilde{GW}_1(X)+c\cdot GW_0(X).$$
We notice that the genus zero contribution to this formula comes from the boundary component with a single rational tail of degree $d$, while elliptic bridges and degenerate contributions with more rational tails do not matter to the genus one Gromov-Witten count. This suggests that removing the component with elliptic tails would provide a more direct and efficient definition of reduced invariants. We plan to do so by comparing the ordinary space of stable maps with Viscardi's space of 1-stable maps.
\end{comment}

\section{The comparison morphism}

%In this section we start investigating the Gromov- Witten type invariant obtained from Viscardi compactification studying the case $m=1$: the source curve is at worst cuspidal. We will see how in this case we can give a comparison with the GW-invariant and explain why the same technique does not work for higher $m$.
%The first thing we do is the following:
%we introduce a moduli space of stably-weighted, prestable, at worst cuspidal, marked curves. We show that there is a birational morphism from a correspondingly decorated moduli space of prestable nodal curves. Taking the fiber product with Viscardi's moduli space of stable cuspidal maps, we show that the resulting space includes in the usual Kontsevich's moduli space, precisely avoiding the component with elliptic tails $D_{\{d\},\{n\}}(X,d)$.

%Why should such a morphism on decorated prestable curves exist? 
%Consider an elliptic tail $C$; a one-dimensional family $\mathcal C$  with central fiber $\mathcal C_0\cong C$ will either be locally constant or smoothen the node. In the first case we can associate to this the locally constant family of cusps obtained by forgetting the elliptic tail and contracting a length-two infinitesimal neighborhood of the node in the rational component; in the second case, we claim that the line bundle $\mathcal O_\mathcal C(3q)$ gives a morphism to a smoothing of the cuspidal $\PP^1$. This heuristics (i.e. being able to substitute an elliptic tail with a cusp over points or DVR schemes) motivates us to believe we can define a morphism from suitably defined moduli spaces of nodal genus one curves to cuspidal curves (cfr. \cite[Lemma 4.2]{SMY2}). In fact we shall extend \cite[Corollary 4.5]{SMY2} to an appropriate setup of moduli stacks of weighted prestable curves. Assume $d>0$ throughout the following.
In this section: we show in two different ways that there exists a morphism at the level of weighted prestable curves $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1);$ introduce the spaces 
\[\Z:= \mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M_{1,n}(\PP^4,d)(1),\qquad \Zp:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M^p_{1,n}(\PP^4,d)(1) \]
 and  and see their relation, respectively, with the moduli space of stable maps, stable maps with fields; use the morphism at the level of prestable curves to induce obstruction theories on $\Z$ and $\Zp.$

@@

\subsection{Fiber products and induced obstruction theories}
Let $\Z$ be defined by the pullback diagram:
\bcd
\mathcal Z \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
\mathfrak M_1^{\rm{wt}}\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
\ecd

@@

We introduce some more spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
\bcd
\mathcal Z^p \ar[r,"\alpha"]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
\XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1^{(1)} \ar[d] \\
\X\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
\ecd

@@

\begin{cor}
$\deg[\Z^p]^{\rm{vir}}_{\rm{loc}}=\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}$
\end{cor}

\section{Local equations and desingularisation}\label{sec:equations}
\subsection{Equations for $\Z^p$ relative to $\XP$}
We are going to need a description of the normal cone $\mathfrak C_{\Z^p/\XP}$ in order to perform a splitting.
